Financial markets for reaching ``green" targets: Cap-and-trade strategies in the Chilean electricity sector

### 2020-04-24 draft_paper/draft_v1.tex
orden paquetes repetidos

\begin{figure}[ht!]
 \includegraphics[width=\textwidth]{draft_paper/Figures/Figure1_comp.png}
 \caption{\color{red}Panel (a): The outer ring shows the production percentage over the total electricity production in 2018 for each technology  obtained from the calibration of our model. The inner ring shows the real operation data for that year. Panel (b): Production levels per technology in the period 2019-2050 for our base-case scenario in our model, that is, business-as-usual, no green policies planned or implemented. }
  \label{fig:bc}
  \end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=5in]{draft_paper/Figures/cap_ext.png}
 \caption{Emission data for Chile from Climate Action Tracker website, historical and projected. See text for details}
  \label{fig:cap}
  \end{figure}

@@

\begin{figure}[hbtp]
\includegraphics[height=\textheight]{draft_paper/Figures/Q_second_cap.png}
 \caption{Production levels per technology for the period 2019-2050 at different emission caps}
  \label{fig:prod_cap}
\end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=4.5in]{draft_paper/Figures/figure4.png}
 \caption{Percentage of power generation from NCRE sources in the period 2019-2050 at different carbon budgets. }
  \label{fig:ernc_percent_cap}
  \end{figure}

@@

In a competitive setting, (exogenous) restrictions as the one given by a quota were introduced by Cass (1984). Endogenous restrictions are analyzed in Cass et al. (2001), Carosi et al. (2009) among others. Nevertheless, the case of endogenous investment restrictions was not included until CE-TM (2018). Here, we limit a long position in the permits market by a proportion of the permits bought int the first stage. Moreover, the endogenous cap can be targeted to specific technologies (segmentation).

The results of the consideration of such constraints segmenting Coal

@@

\begin{figure}[ht]
    \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{draft_paper/Figures/demand_scenarios.png}
    \caption{}
  \label{fig:demand_scn}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{draft_paper/Figures/mean_prices_scenarios.png}
    \caption{ }
  \label{fig:mean_price}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{draft_paper/Figures/price_allowances.png}
    \caption{  }
  \label{fig:price_allo}
  \end{subfigure}
    \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{draft_paper/Figures/prices_trading_scenarios.png}
    \caption{}
  \label{fig:price_trade}
  \end{subfigure}\quad
   \caption{Panel (a): Demand scenarios. Panel (b): Electricity prices per MWh, for each carbon budget value and different demand scenarios. Panel (c): Price of allowances per ton CO$_2e$ for each carbon budget. Panel (d): Allowance trading price per ton CO$_2e$ for each carbon budget and different demand scenarios. Color legend for Panels (b) and (d) are the same as in Panel (a).}
\end{figure}

@@

\begin{figure}[ht]
\centering
    \includegraphics[width=5.5in]{draft_paper/Figures/auxiliar.png}
\caption{Production levels per technology for the period 2019-2050 for different carbon budgets.  Demand scenario : High GDP.}
  \label{fig:comp_100_1000}
\end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=4.5in]{draft_paper/Figures/ernc_percent_shadows.png}
 \caption{Percentage of power generation from NCRE sources for different carbon budgets. The shaded areas represent the range between the highest demand scenario (High GDP) and the lowest (High Effort). The dash and dash-dot lines mark the level at 60\% and 70\% of NCRE sources.}
  \label{fig:ernc_percent_shadows}
  \end{figure}

>>>>

\begin{figure}[ht!]
 \includegraphics[width=\textwidth]{Figures/Figure1_comp.png}
 \caption{\color{red}Panel (a): The outer ring shows the production percentage over the total electricity production in 2018 for each technology  obtained from the calibration of our model. The inner ring shows the real operation data for that year. Panel (b): Production levels per technology in the period 2019-2050 for our base-case scenario in our model, that is, business-as-usual, no green policies planned or implemented. }
  \label{fig:bc}
  \end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=5in]{Figures/cap_ext.png}
 \caption{Emission data for Chile from Climate Action Tracker website, historical and projected. See text for details}
  \label{fig:cap}
  \end{figure}

@@

\begin{figure}[hbtp]
\includegraphics[height=\textheight]{Figures/Q_second_cap.png}
 \caption{Production levels per technology for the period 2019-2050 at different emission caps}
  \label{fig:prod_cap}
\end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=4.5in]{Figures/figure4.png}
 \caption{Percentage of power generation from NCRE sources in the period 2019-2050 at different carbon budgets. }
  \label{fig:ernc_percent_cap}
  \end{figure}

@@

In a competitive setting, (exogenous) restrictions as the one given by a quota were introduced by \cite{Cass1984,Cass2006}. Endogenous restrictions are analyzed in \cite{Cassetal2001,Carosietal2009} among others. Nevertheless, the case of endogenous investment restrictions was not included until \cite{cea-echenique_general_2018}.

We analize the impact of an endogenous limit for the long position in the permits market. The cap is defined by a proportion of the permits bought in the first stage. The endogenous cap can be targeted to a specific technologies (segmentation).

The application of a targeted policy to segment the Coal-based technology implies in the elimination of the technology by 2035 if the proportion is 70\%.

@@

\begin{figure}[ht]
    \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Figures/demand_scenarios.png}
    \caption{}
  \label{fig:demand_scn}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Figures/mean_prices_scenarios.png}
    \caption{ }
  \label{fig:mean_price}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Figures/price_allowances.png}
    \caption{  }
  \label{fig:price_allo}
  \end{subfigure}
    \begin{subfigure}[t]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Figures/prices_trading_scenarios.png}
    \caption{}
  \label{fig:price_trade}
  \end{subfigure}\quad
   \caption{Panel (a): Demand scenarios. Panel (b): Electricity prices per MWh, for each carbon budget value and different demand scenarios. Panel (c): Price of allowances per ton CO$_2e$ for each carbon budget. Panel (d): Allowance trading price per ton CO$_2e$ for each carbon budget and different demand scenarios. Color legend for Panels (b) and (d) are the same as in Panel (a).}
\end{figure}

@@

\begin{figure}[ht]
\centering
    \includegraphics[width=5.5in]{Figures/auxiliar.png}
\caption{Production levels per technology for the period 2019-2050 for different carbon budgets.  Demand scenario : High GDP.}
  \label{fig:comp_100_1000}
\end{figure}

@@

\begin{figure}[ht!]
\centering
 \includegraphics[width=4.5in]{Figures/ernc_percent_shadows.png}
 \caption{Percentage of power generation from NCRE sources for different carbon budgets. The shaded areas represent the range between the highest demand scenario (High GDP) and the lowest (High Effort). The dash and dash-dot lines mark the level at 60\% and 70\% of NCRE sources.}
  \label{fig:ernc_percent_shadows}
  \end{figure}
